Physics-informed machine learning of reduced-order model

### 2020-06-21 manuscript/elsarticle/manuscript.tex
pc

\usepackage{amsthm,amsmath,amssymb}
\usepackage{mathrsfs}

%\usepackage{refcheck} % check the reference of equations, figures, tables and citations

@@

\section{Physics-informed machine learning of reduced-order model}
This section presents several methods aiming to find the mapping from parameter space to high-fidelity solution. Based on the reduced basis, we jsut need to find the mapping from parameter space to reduced basis coefficient, namely the projection of high-fidelity solution onto reduced basis.
These methods are classified into intrusive and non-intrusive methods. We term it as a non-intrusive method if the reduced-order model won't need to be built, otherwise it is an intrusive method. As for non-intrusive methods in reference ??, the underlying idea is an interpolation, such as cubic spline method based on a tensor-product grid in parameter space and building an artificial neural network (ANN) with a labeled data. These non-intrusive methods can achieve a good approximation and very little online cost, but the drawback is their highly relying on the size of labeled data, namely the number of evaluations of full-order model. According to Jan, artificial neural network has a good reduction in the eagerness of more labeled data compared with the cubic spline method. Even so, the required size of labeled data is prohibitively larger than the size of snapshots for building a satisfactory reduced basis. A good alternate is the intrusive method, where the reduced-order model is solved with a suitable nonlinear solver, such as Newton-like method. However, it is also a tough work to find the right solution especially for a larger $m$. To this end, we combine ANN and the reduced-order model together together.

In the next subsections, we first briefly introduce the basis idea of artificial neural networks. Then we will start from the projection-driven neural networks proposed by Jan ??. After that two methods, namely the physics-inform neural network and physics-reinforced neural network are proposed, pursue a higher prediction accuracy with fewer snapshots.

\subsection{Artificial neural network (ANN) }
For an arbitrary target function, ANN is a powerful nonlinear approximators constituted of a linear combination of some nonlinear functions. Generally, ANN contains $L$ hidden layers besides input and output layers,  the $i$th layer equipped with $n_l$ neurons, where $l=0,1,..L,L+1$ denotes the input layer, 1st hidden layer,..., $L$th hidden layer and the output layer, respectively. ANN is a nonlinear function $\mathcal{O}: \mathbf{R}^{n_0} \mapsto \mathbf{R}^{n_{L+1}}$ of inputs $\mathbf{x}$, comprising a  recursion
\begin{equation}
\left \{
\begin{aligned}
&\mathcal{O}^{0}   = \mathbf{x} \\
&\mathcal{O}^{l}   = \sigma ^{l} \left( \mathbf{W}^{l} \mathcal{O}^{l-1} + \mathbf{b}^{l}
\right)
\qquad 1 \le l \le L+1
\end{aligned}
\right.
\end{equation}
where $\mathcal{O}^{l} \in \mathbf{R}^{n_l}$ is the output of $l$th layer, $n_0$ is the input dimension and $n_{L+1}$ is the output dimension, $\mathbf{W}^{l} \in \mathbf{R}^{n_{l} \times n_{l-1}}$ is the weights, $\mathbf{b}^{l} \in \mathbf{R}^{n_l}$ is the biases and $\sigma ^{l}$ is an element-wise activation function. Usually, the activation function of the output layer is just set as the identification function, namely $\sigma ^{L+1}\left(\mathbf{x}\right)=\mathbf{x}$, while the activation function of all hidden layers are set as a same nonlinear function.

@@

\subsection{Training the networks}
%To get a good mapping form parameter $\pmb{\mu} \in \mathcal{P}$ to the projection of snapshot $\pmb{\phi}_h \in \mathbf{R}^{N}$ in reduced sapce, a ANN is built and trained based on reduced basis.

Some preparation need to be made before training the networks. Recall that the snapshot set $\pmb {\Phi}_{\mathcal{P}_M}=\{\pmb{\phi}_h(\pmb{\mu}_1), \pmb{\phi}_h(\pmb{\mu}_2),...,\pmb{\phi}_h(\pmb{\mu}_M)\}  \in \mathbf{R}^{N \times M}$ corresponding with the parameter set $\mathcal{P}_M=\{\pmb{\mu}_1, \pmb{\mu}_2,...,\pmb{\mu}_M\} \subset \mathcal{P}$ is employed to extract the reduced basis $\mathbf{V}$ , according to Section \ref{sec_ROM}. Due to the orthogonality of $\mathbf{V}$, the projection coefficient of each snapshot on the reduced space is derived by left multiplying Eq. (\ref{eq_projection}) with $\mathbf{V}^T$
\begin{equation}
\begin{aligned}
\pmb{\alpha}  &   =    \mathbf{V}^T (\pmb{\phi}_h -\tilde{\phi} - \pmb{\epsilon}) \\
              &\approx \mathbf{V}^T (\pmb{\phi}_h -\tilde{\phi})
\end{aligned}
\label{eq_RBCoefficients}
\end{equation}

@@

\subsubsection{physics-informed neural network(PINN)}
Due to the limited number of available snapshots, it is always difficult to train a good network with Projection-driven neural network. Luckily, we have the reduced-order model, an another choice for training an ANN. Given the reduced-order model, ANN outputs don't explicitly approximate some given targets, but just do satisfy the reduced-order model. In this way, no target is needed, and thus we have unlimited training data. By Latin hypercube sampling in parameter space, we generate the data set $\mathcal{D}_{Resi}=\{ \pmb{\mu}_i\}_{i=1}^{M_{Resi}}$, constraining $M_{Resi}$ residual points in parameter space. The loss function is defined as follows
\begin{equation}
{loss}_{\rm{PINN}} = \frac{1}{N_{\cal D}}
{{\sum\limits_{\pmb\mu  \in {\cal D}}
{ \left\|
ROM \left(\widetilde {\cal O}\left( {\pmb\mu ;{\bf{W}},{\bf{b}}} \right) \right)
\right \|^2}
}}
\end{equation}
where $ROM(\pmb{\alpha})=\mathbf{V}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)$
is the reduced-order model defined in Eq. (\ref{eq_Galerkin}).
As we have unlimited training data, there is no problem of overfitting and thus no need of validation data set.  The bottleneck of training the physics-informed neural network is how to handle the local minima trap. Here, we adopt the Mini-Batch training method, where the data set are shuffled and randomly in to serval non-overlap subsets in each epoch. With each subset, the weights and biases will be updated by optimizer. The Mini-Batch training method can effectively avoid local minima trap and has enjoyed a great number of applications.

\subsubsection{physics-reinforced neural network(PRNN)}
\label{PRNN}
Physics-informed neural network(PINN) seems an perfect potential in prediction reduced basis coefficients. But the numerical experiments show that  the accuracy of the physics-informed neural network sometimes is not that good, even if the the corresponding loss drops down to a very low level. The underlying reason comes from that the large scale difference of different RB modes.
First, the RB mode with smaller index will be more dominant to the residual of the reduced-order model. Second, the training of network cannot work like a deterministic nonlinear solver, and it can only reduce the loss to a moderate level. Thus, the reduced-order model cannot be well-solved thorough training network. As a result, the optimizer tends to neglect the relatively unimportant modes, namely the high-index modes.

To address this problem, we add the projection RB coefficients into the loss function of PINN. Although the projection RB coefficients are always not the solutions of the reduced-order model, the projections are more close to the snapshots and thus full-order model. Besides, the projection RB coefficients can be calculated directly according to Eq. \ref{eq_RBCoefficients}, and it has no problem of domination for different modes. Therefore, the projection RB coefficients can be used to provide more physical information into the network training. Thus we name this method as physics-reinforced neural network. The loss function is defined as the weighted sum of those of PDNN and PINN, namely
\begin{equation}
{loss}_{\rm{PRNN}} =
\left. {{loss}_{\rm{PDNN}}} \right|_{{\cal{D}} = {\cal {D}}_{Pr} }
+
w \times \left. {{loss}_{\rm{PINN}}} \right|_{{\cal D} = {\cal D}_{Resi }}
\end{equation}
where $w$ is a specific weight balancing projection and reduced-order model. In this work, we find that simply setting $w=1$ will produces a good result.  When training the network, the two data sets are treated separately. As for projection data set ${\cal D}_{Pr}$, it is more accurate but its size is very small, so we continue to use full batch. As for residual data set ${\cal D}_{Pr}$, it is less accurate but its size is very large, and we use mini-batch method for each updating of the network.

\section{Numerical results}
In this section, the following notations will be used repeatedly in the text and plots to distinguish results of different methods:
we will discuss the application of PDNN, PINN and PRNN methods to three parameterized PDEs, namely the one-dimensional Burges' equation, two-dimensional lid driven flow and two-dimensional natural convection flow. For comparison of accuracy, the results of two analytical methods are also considered:
\begin{enumerate}[(1)]
\item \textbf{Projection}: Projection of high-fidelity solution onto reduced basis;
\item \textbf{POD-G}: The solution of the reduced-order model.
\end{enumerate}
The one-dimensional case are designed with an artificial solution with a zero-value boundary condition, intended for testing the prediction accuracy of the three networks and also study the influence of several factors. Their prediction accuracy are further discussed the two realistic flow problems, where geometry parameters and common boundary conditions (Dirichlet and Neumann) are included.

To assess the online accuracy of these methods, the following metrics are defined in the sense of mean squared error.
\begin{enumerate}[(1)]
\item the average relative error of  projections
\begin{equation}
\varepsilon_{\rm{Proj}}
=\frac{1}{N_{{\cal D}_{te}}}
\sum\limits_{\pmb\mu ,\pmb{\phi}_h  \in {{\cal D}_{te}}}{
\frac{\left\| \pmb{\phi}_h - \tilde{\phi} -\mathbf{V}\mathbf{V}^T \left( \pmb{\phi}_h - \tilde{\phi} \right)  \right\|}
{\left\| \pmb{\phi}_h - - \tilde{\phi} \right\|}
}
\end{equation}

@@

\end{enumerate}
where ${{\cal D}_{te}}=\{\pmb{\mu}_i, \pmb{\phi}_h(\pmb{\mu}_i)\}_{i=1}^{N_{{\cal D}_{te}}}$ is the test data set, the subscript "$\bullet$" is used to take the place of "POD-G","PDNN","PINN" and "PRNN". Thus ,$\pmb{\alpha}_{\bullet}\left( \pmb{\mu}\right)$ is the solution calculated from the corresponding method.

Note that Projection, POD-G, PDNN, PINN and PRNN are all coded in Python. The networks built are are all under the framework of Pytorch. The training of networks are all  implemented on two GUPs (NVIDIA Quadro GP100) of a server class station. To solve the reduced-order model directly for POD-G, the solver "linalg.solve" in  Numpy library is employed. We refer the reader to the repository \footnote{available at \url{https://github.com/cwq2016/POD-PINN}} for further details of the code method. For more information of the code, we refe For different data set as discussed above, we employ the specific sampling methods in parameter space: for building the RB, we adopt the Sobol sequences, a quasi-random low-discrepancy sequences; For choosing residual points, we use the Latin hypercube sampling; For generating test data set, we employ uniformly tensor-product grid.

To train the netwroks

\subsection{Burgers' equation}
In this subsection, to validate the proposed methods, we consider the one-dimensional parameterized Burges' equation.
\begin{equation}
\left\{
\begin{aligned}
	 &\phi(x;\pmb{\mu}) \cdot \nabla \phi(x;\pmb{\mu}) -  \Delta \phi(x;\pmb{\mu})= s(x;\pmb{\mu})  \qquad -1 \le x \le 1\\
	 &\phi\left ( x= \pm1; \pmb {\mu} \right ) = 0
\end{aligned}\right.
\end{equation}
where $\pmb{\mu} =(\mu_1, \mu_2) \in [1,10] \times [1,10]$ and $s(x;\pmb{\mu})$ it the source term defined so that the exact solution is
\begin{equation}
	\phi(x; \pmb{\mu}) = (1+\mu_1 x)\sin(-\mu_2 x/3) (x^2-1) .
\end{equation}
The solution at the two end points are simply set zero to avoid the influence of boundary conditions. The problem is solved with Chebyshev pseudospectral(PS) method with $N_p+1$=128+1 Chebyshev Gauss-Lobatto points.

We are are interested in the prediction accuracy of   Projection, POD-G, PDNN, PINN and PRNN methods. The accuracy of Projection and POD-G is only determined by two factors, namely the sample size for building RB and and the number of chosen modes, given that the nonlinear solver for POD-G is accurate enough. Here we term the two factors as essential factors.
Besides the two factors, neural network like PDNN, PINN and PRNN are also determined by network architecture, the number of residual points, and so on. To study the influence of these factors, we resort to the control variates method. Some base values are set for these factor, namely sample size is $N_s=80$, the number of chosen modes is picked from the set $\{2,3,...,9\}$,  network architecture is $L=3$ and $n_H=20$, the number of residual points $N_{Resi}=5000$. To test the prediction accuracy, a test data set of size $101 \times 101=10201$ is generated on a tensor-product parameter grid $\{1+ 0.09i\}_{i=0}^{i=100} \times \{1+ 0.09i\}_{i=0}^{i=100}$. The dense test grid will grantee the reliability of the prediction accuracy.

We first study the influence of the sample size. Fig. ??, presents the singular value distribution for the sample number $N_s=80$. It is shown that the singular value decays quickly, implying that  a small number of RB modes is enough for representing the dynamic of the problem. Meanwhile, the sample number can also be largely reduced. Thus, for comparison, $N_{s}=10$ and 320 random parameter samples are independently generated with Sobol sequences. The five methods are applied to the problem after the RB are built for $N_{s}=10$, 80 and 320, respectively. The prediction accuracy is shown in Fig. ??. It is shown that the Projection enjoys a better accuracy compared with the POD-G, but their discrepancy is very small. The pojection/POD-G improves just a little for sample number $N_s$ increasing from 10 to 80, and almost stagnates from $N_s=80$ to 320. Thus, sample number $N_s=10$ is enough for capture the main dynamic of the problem. The networks perform quite differently. The accuracy of PDNN is far lower than that of PINN and PRNN. Even with the increase of sample number, the accuracy of PDNN can improve by one order of magnitude, but the error curves fluctuate intensively especially for larger $m$. On the contrary, both PINN and PRNN perform much better, they almost keep pace with POD-G for smaller $m$. As $M \ge 6$, the PINN performs a little better than the PRNN, but their error level both come to a flat and cannot further drop down. The reason for the flat level is that both PINN and PRNN can only reduce their loss function down to a level of $10^{-6}$ for this problem rather zero or machine zero level. Thus the high-index modes are neglected by the networks.  The PINN performs a little better than the PRNN, it is opponent with our inference in Section \ref{PRNN}. The reason is two-fold: first, the problem and the target function is relatively easy for networks; second, the accuracy of POD-G is very close to projection. Therefore, There is no priority for the PRNN, as its loss function is a hybrid.

To further study the influence of network architecture on the prediction accuracy of networks, we change the network width to $n_H=10$ and $n_H=30$,respectively, while keeping the network depth $L=3$ fixed. The results are shown in Fig. ??. It is shown that the PDNN can not gain an improvement of accuracy with the increase of $n_H$, or even get rid of the fluctuation, resulting from the overfitting trap. On the contrary, the PINN and PRNN show a much better tendency. Their prediction accuracy increases with $n_H$ but tends to saturate for a larger $n_H$. This is in accordance with the situation that the approximation capability of the network increases and gradually saturate with network size.

As there is unlimited residual points for training PINN and PRNN, we are interested in how the number of residual points influence the prediction accuracy. Apart from $N_{Resi}=5000$, the numbers of residual points $N_{Resi}=1250$, $2500$ and $10000$ are considered, and their results are shown in Fig. ??. The influence of the numbers of residual points is similar with that of network architecture.

>>>>

\usepackage{amsthm,amsmath,amssymb}
\usepackage{mathrsfs}
%\usepackage[section]{placeins}
%\usepackage{refcheck} % check the reference of equations, figures, tables and citations

@@

\section{Physics-informed machine learning of reduced-order model}
This section presents several methods aiming to find the mapping from parameter space to high-fidelity solution. Based on the reduced basis, we just need to find the mapping from parameter space to reduced basis coefficient, namely the projection of high-fidelity solution onto reduced basis.
These methods are classified into intrusive and non-intrusive methods. We term it as a non-intrusive method if the reduced-order model won't need to be built, otherwise it is an intrusive method.
As for non-intrusive methods in reference ??, the underlying idea is an interpolation, such as the projection-driven neural network(PDNN) proposed by Jan ?? and the traditional cubic spline method. These non-intrusive methods can achieve a good approximation with very little online cost, but the drawback is their highly relying on the size of labeled data set, namely the number of evaluations of full-order model.
For example, the traditional cubic spline method requires high-fidelity solutions with a tensor-product grid in parameter space, and the POD-NN are trained with a labeled data set.
According to Jan, the PDNN has a good reduction in the eagerness of more labeled data compared with the cubic spline method.
Even so, the required size of labeled data for the PDNN is prohibitively larger than the size of snapshots for building a satisfactory reduced basis.

A good alternate is the intrusive method, feathering a much cheaper computational cost of the reduced-order model. One can directly solve the reduced-order model with a suitable nonlinear solver, such as Newton-like method. However, it is also a tough work to find the right solution especially for a larger number of reduced-order model, as a reasonable initial solution is not always available. To this end, we combine artificial network (ANN) and the reduced-order model together together, benefiting from the cheap cost of reduced-order mode and powerful approximating capability of ANN. We first propose to solve the reduced-order model with ANN, referred to physics-informed network (PINN). Then we try to add more prior knowledge into reinforce the PINN, referred to physics-reinforced neural network (PDNN). For the sake of clarity, the relationships of these methods are illustrated in Fig. \ref{fig_relationship}.
\begin{figure}[!ht]
  \centering
  \includegraphics[width=12cm]{../fig/RelationshipChart.pdf}
\caption{Relationship among methods}
\label{fig_relationship}
\end{figure}

In the next subsections, we first briefly introduce the basic idea of artificial neural networks. Then we will start from the projection-driven neural networks proposed by Jan ??. After that, the proposed physics-inform neural network and physics-reinforced neural network will be detailed.

\subsection{Artificial neural network (ANN) }
For an arbitrary target function, ANN is a powerful nonlinear approximator constituted of a linear combination of some nonlinear functions. Generally, ANN contains $L$ hidden layers besides input and output layers,  the $i$th layer equipped with $n_l$ neurons, where $l=0,1,..L,L+1$ denotes the input layer, 1st hidden layer,..., $L$th hidden layer and the output layer, respectively. ANN is a nonlinear function $\mathcal{O}: \mathbf{R}^{n_0} \mapsto \mathbf{R}^{n_{L+1}}$ of inputs $\mathbf{x}$, comprising a  recursion
\begin{equation}
\left \{
\begin{aligned}
&\mathcal{O}^{0}   = \mathbf{x} \\
&\mathcal{O}^{l}   = \sigma ^{l} \left( \mathbf{W}^{l} \mathcal{O}^{l-1} + \mathbf{b}^{l}
\right)
\qquad 1 \le l \le L+1
\end{aligned}
\right.
\end{equation}
where $\mathcal{O}^{l} \in \mathbf{R}^{n_l}$ is the output of $l$th layer, $n_0$ is the input dimension and $n_{L+1}$ is the output dimension, $\mathbf{W}^{l} \in \mathbf{R}^{n_{l} \times n_{l-1}}$ is the weights, $\mathbf{b}^{l} \in \mathbf{R}^{n_l}$ is the biases and $\sigma ^{l}$ is an element-wise activation function. Usually, the activation function of the output layer is just set as the identification function, namely $\sigma ^{L+1}\left(\mathbf{x}\right)=\mathbf{x}$, while the activation function of all hidden layers are set as a same nonlinear function.

@@

\subsection{Customized networks}
%To get a good mapping form parameter $\pmb{\mu} \in \mathcal{P}$ to the projection of snapshot $\pmb{\phi}_h \in \mathbf{R}^{N}$ in reduced sapce, a ANN is built and trained based on reduced basis.

Some preparation need to be made before introducing the networks. Recall that the snapshot set $\pmb {\Phi}_{\mathcal{P}_M}=\{\pmb{\phi}_h(\pmb{\mu}_1), \pmb{\phi}_h(\pmb{\mu}_2),...,\pmb{\phi}_h(\pmb{\mu}_M)\}  \in \mathbf{R}^{N \times M}$ corresponding with the parameter set $\mathcal{P}_M=\{\pmb{\mu}_1, \pmb{\mu}_2,...,\pmb{\mu}_M\} \subset \mathcal{P}$ is employed to extract the reduced basis $\mathbf{V}$ , according to Section \ref{sec_ROM}. Due to the orthogonality of $\mathbf{V}$, the projection coefficient of each snapshot on the reduced space is derived by left multiplying Eq. (\ref{eq_projection}) with $\mathbf{V}^T$
\begin{equation}
\begin{aligned}
\pmb{\alpha}  &   =    \mathbf{V}^T (\pmb{\phi}_h -\tilde{\phi} - \pmb{\epsilon}) \\
              &\approx \mathbf{V}^T (\pmb{\phi}_h -\tilde{\phi})
\end{aligned}
\label{eq_RBCoefficients}
\end{equation}

@@

\subsubsection{Physics-informed neural network(PINN)}
Due to the limited number of available snapshots, it is always difficult to train a good network with Projection-driven neural network. Luckily, we have the reduced-order model, an another choice for training an ANN. Given the reduced-order model, ANN outputs don't explicitly approximate some given targets, but just do satisfy the reduced-order model. In this way, no target is needed, and thus we have unlimited training data. By Latin hypercube sampling in parameter space, we generate the data set $\mathcal{D}_{Resi}=\{ \pmb{\mu}_i\}_{i=1}^{M_{Resi}}$, constraining $M_{Resi}$ residual points in parameter space. The loss function is defined as follows
\begin{equation}
{loss}_{\rm{PINN}} = \frac{1}{N_{\cal D}}
{{\sum\limits_{\pmb\mu  \in {\cal D}}
{ \left\|
ROM \left(\widetilde {\cal O}\left( {\pmb\mu ;{\bf{W}},{\bf{b}}} \right) \right)
\right \|^2}
}}
\end{equation}
where $ROM(\pmb{\alpha})=\mathbf{V}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)$
is the reduced-order model defined in Eq. (\ref{eq_Galerkin}).
As we have unlimited training data, there is no problem of overfitting and thus no need of validation data set.  The bottleneck of training the physics-informed neural network is how to handle the local minima trap. Here, we adopt the Mini-Batch training method, where the data set are shuffled and randomly in to serval non-overlap subsets in each epoch. With each subset, the weights and biases will be updated by optimizer. The Mini-Batch training method can effectively avoid local minima trap and has enjoyed a great number of applications.

\subsubsection{Physics-reinforced neural network(PRNN)}
\label{PRNN}
Physics-informed neural network(PINN) seems an perfect potential in prediction reduced basis coefficients. But the numerical experiments show that  the accuracy of the physics-informed neural network sometimes is not that good, even if the the corresponding loss drops down to a very low level. The underlying reason comes from that the large scale difference of different RB modes.
First, the RB mode with smaller index will be more dominant to the residual of the reduced-order model. Second, the training of network cannot work like a deterministic nonlinear solver, and it can only reduce the loss to a moderate level. Thus, the reduced-order model cannot be well-solved thorough training network. As a result, the optimizer tends to neglect the relatively unimportant modes, namely the high-index modes.

To address this problem, we add the projection RB coefficients into the loss function of PINN. Although the projection RB coefficients are always not the solutions of the reduced-order model, the projections are more close to the snapshots and thus full-order model. Besides, the projection RB coefficients can be calculated directly according to Eq. \ref{eq_RBCoefficients}, and it has no problem of domination for different modes. Therefore, the projection RB coefficients can be used to provide more physical information into the network training. Thus we name this method as physics-reinforced neural network. The loss function is defined as the weighted sum of those of PDNN and PINN, namely
\begin{equation}
{loss}_{\rm{PRNN}} =
\left. {{loss}_{\rm{PDNN}}} \right|_{{\cal{D}} = {\cal {D}}_{Pr} }
+
w \times \left. {{loss}_{\rm{PINN}}} \right|_{{\cal D} = {\cal D}_{Resi }}
\label{eq_lossPRNN}
\end{equation}
where $w$ is a specific weight balancing projection and reduced-order model. In this work, we find that simply setting $w=1$ will produces a good result.  When training the network, the two data sets are treated separately. As for projection data set ${\cal D}_{Pr}$, it is more accurate but its size is very small, so we continue to use full batch. As for residual data set ${\cal D}_{Pr}$, it is less accurate but its size is very large, and we use mini-batch method for each updating of the network.

\section{Numerical results}
In this section,
we will discuss the application of PDNN, PINN and PRNN methods to the parameterized PDEs, namely the one-dimensional Burges' equation, two-dimensional lid driven flow and two-dimensional natural convection flow.
The one-dimensional case are designed with an artificial solution with a zero-value boundary condition, intended for testing the prediction accuracy of the three networks and also study the influence of several factors. Their prediction accuracy are further discussed the two realistic flow problems, where geometry parameters and common boundary conditions (Dirichlet and Neumann) are included.

For comparison of accuracy, the results of two analytical methods are also considered:
\begin{enumerate}[(1)]
\item \textbf{Projection}: Projection of high-fidelity solution onto reduced basis;
\item \textbf{POD-G}: The solution of the reduced-order model.
\end{enumerate}
As the PDNN is trained with the projection coefficients of high-fidelity, the PDNN targets the accuracy of the Projection. The PINN is trained to meet the reduced-order model, the PINN targets the accuracy the POD-G. The PRNN can be viewed as a blending of the PDNN and PINN, and thus its accuracy is expected to fall somewhere between those of the Projection and POD-G.

To assess the online accuracy of these methods, the following metrics are defined in the sense of mean squared error.
\begin{enumerate}[(1)]
\item the average relative error of  projections
\begin{equation}
\varepsilon_{\rm{Proj}}
=\frac{1}{N_{{\cal D}_{te}}}
\sum\limits_{\pmb\mu ,\pmb{\phi}_h  \in {{\cal D}_{te}}}{
\frac{\left\| \pmb{\phi}_h - \tilde{\phi} -\mathbf{V}\mathbf{V}^T \left( \pmb{\phi}_h - \tilde{\phi} \right)  \right\|}
{\left\| \pmb{\phi}_h  - \tilde{\phi} \right\|}
}
\end{equation}

@@

\end{enumerate}
where ${{\cal D}_{te}}=\{\pmb{\mu}_i, \pmb{\phi}_h(\pmb{\mu}_i)\}_{i=1}^{N_{{\cal D}_{te}}}$ is the test data set of size ${{\cal D}_{te}}$, the subscript "$\bullet$" is used to take the place of "POD-G","PDNN","PINN" and "PRNN". Thus, $\pmb{\alpha}_{\bullet}\left( \pmb{\mu}\right)$ is the solution calculated from the corresponding method.

Note that the Projection, POD-G, PDNN, PINN and PRNN methods are all coded in Python. The networks built are are all under the framework of Pytorch. The training of networks are all  implemented on two GUPs (NVIDIA Quadro GP100) of a server class station. To solve the reduced-order model directly for POD-G, the nonlinear solver "linalg.solve" in  Numpy library is employed. We refer the reader to the repository \footnote{available at \url{https://github.com/cwq2016/POD-PINN}} for further details of the code method. For different data set as discussed above, we employ the specific sampling methods in parameter space: for building the RB, we adopt the Sobol sequences, a quasi-random low-discrepancy sequences; For choosing residual points, we use the Latin hypercube sampling; For generating test data set, we employ uniformly tensor-product grid.

\subsection{Burgers' equation}
In this subsection, to validate the proposed methods, we consider the one-dimensional parameterized Burges' equation.
\begin{equation}
\left\{
\begin{aligned}
	 &\phi(x;\pmb{\mu}) \cdot \nabla \phi(x;\pmb{\mu}) -  \Delta \phi(x;\pmb{\mu})= s(x;\pmb{\mu})  \qquad -1 \le x \le 1\\
	 &\phi\left ( x= \pm1; \pmb {\mu} \right ) = 0
\end{aligned}\right.
\end{equation}
where $\pmb{\mu} =(\mu_1, \mu_2) \in [1,10] \times [1,10]$ and $s(x;\pmb{\mu})$ is the source term defined so that the exact solution satisfies
\begin{equation}
	\phi(x; \pmb{\mu}) = (1+\mu_1 x)\sin(-\mu_2 x/3) (x^2-1) .
\end{equation}
For each parameter, the solution at the two end points are simply set zero to avoid the influence of boundary conditions. The problem is solved with Chebyshev pseudospectral(PS) method with $N_p+1$=128+1 Chebyshev Gauss-Lobatto points.

We are are interested in the prediction accuracy of the Projection, POD-G, PDNN, PINN and PRNN methods. The accuracy of Projection and POD-G is only determined by two factors, namely the sample size $N_s$ for building RB and and the number of chosen modes $m$, provided that the nonlinear solver for POD-G is accurate enough. Here we term the two factors as essential factors.
Besides the two factors, neural network like PDNN, PINN and PRNN are also determined by network architecture, the number of residual points, and so on. To study the influence of these factors, we resort to the control variates method. Some base values are set for these factor, namely sample size is $N_s=80$, the number of chosen modes is picked from the set $\{2,3,...,9\}$,  network architecture is $L=3$ and $n_H=20$, the number of residual points is $N_{Resi}=5000$. To test the prediction accuracy, a test data set of size $101 \times 101=10201$ is generated on a tensor-product parameter grid $\{1+ 0.09i\}_{i=0}^{i=100} \times \{1+ 0.09i\}_{i=0}^{i=100}$. The dense test grid will guarantee the reliability of the prediction accuracy. As for the training of networks, we use the same following hyperparameters: 20000 epoches, 10 batches with each batch of size $N_{Resi}/10$, the leaning rate initialized as 0.01 and decaying by 96\% every 200 epoches.

We first study the influence of the sample size. Fig. \ref{fig_1DBurgesSingularValues_80}, presents the singular value distribution for the sample number $N_s=80$. It is shown that the singular value decays quickly, implying that  a small number of RB modes is enough for representing the dynamic of the problem. Meanwhile, the sample number can also be largely reduced. Thus, for comparison, $N_{s}=10$ and 320 random parameter samples are independently generated with Sobol sequences. The five methods are applied to the problem after the RB are built for $N_{s}=10$, 80 and 320, respectively. The prediction accuracy is shown in Fig. \ref{fig_1DBurgesErrorComparsion_SampleNum}. It is shown that the Projection enjoys a better accuracy compared with the POD-G, but their discrepancy is very small. The pojection/POD-G improves just a little for sample number $N_s$ increasing from 10 to 80, and almost stagnates from $N_s=80$ to 320. Thus, sample number $N_s=10$ is enough for capture the main dynamic of the problem. The networks perform quite differently. The accuracy of PDNN is far lower than that of PINN and PRNN. Even with the increase of sample number, the accuracy of PDNN can improve by one order of magnitude, but the error curves fluctuate intensively especially for larger $m$. On the contrary, both PINN and PRNN perform much better, they almost keep pace with POD-G for smaller $m$. As $m \ge 6$, the PINN performs a little better than the PRNN, but their error level both come to a saturation and cannot further drop down. The reason for the saturation is that both the PINN and PRNN can only reduce their loss function down to a level of $10^{-6}$ for this problem rather than zero or machine zero level. Thus the high-index modes of little importance are neglected by the networks.  The PINN performs a little better than the PRNN, which is opponent with our inference in Section \ref{PRNN}. The reason is two-fold: first, the problem and the target function is relatively easy for networks; second, the accuracy of POD-G is very close to projection. Therefore, There is no priority for the PRNN, as its loss function is a hybrid.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=9cm]{../../pythonNN/1DBurges/fig/SingularValues_80.pdf}
\caption{Singular value distribution of 80 snapshots for 1D Burges' equation}
\label{fig_1DBurgesSingularValues_80}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=12cm]{../../pythonNN/1DBurges/fig/ErrorComparsion_SampleNum.pdf}
\caption{The prediction accuracy of the Projection, POD-G, PDNN, PINN and PRNN methods for the number of snapshots $N_s$=10, 80 and 320, respectively.}
\label{fig_1DBurgesErrorComparsion_SampleNum}
\end{figure}

To further study the influence of network architecture on the prediction accuracy of the three networks, we change network width to $n_H=10$ and $n_H=30$,respectively, while keeping network depth $L=3$ fixed. The results are shown in Fig. \ref{fig_1DBurgesErrorComparsion_Netsize}. It is shown that the PDNN can not gain an improvement of accuracy with the increase of $n_H$, or even get rid of the fluctuation, resulting from the overfitting trap. On the contrary, the PINN and PRNN show a much better tendency. Their prediction accuracy increases with $n_H$ but tends to saturate for a larger $n_H$. This is in accordance with the situation that the approximation capability of the network increases and gradually saturate with network size.

As there are unlimited residual points available for training both the PINN and PRNN, we are interested in how the number of residual points influence the prediction accuracy. In addition to $N_{Resi}=5000$, the numbers of residual points $N_{Resi}=1250$, $2500$ and $10000$ are considered, and the results are shown in Fig. \ref{fig_1DBurgesErrorComparsion_NResi}. The influence of the number of residual points is similar with that of network architecture. That is to say, the prediction accuracy increases with the number of residual points $N_{Resi}$, but it will reach a saturation after some critical $N_{Resi}$.

Besides, the further confirmation of the reliability of PRNN is shown in Fig. \ref{fig_1DBurgesResultComparsion}, offering a good agreement between the Chebyshev pseudospectral method and PRNN for some specific parameters.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=9cm]{../../pythonNN/1DBurges/fig/ErrorComparsion_Netsize.pdf}
\caption{The prediction accuracy of the Projection, POD-G, PDNN, PINN and PRNN methods. The network width is set $n_H=10$, 20 and 30, respectively.}
\label{fig_1DBurgesErrorComparsion_Netsize}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=9cm]{../../pythonNN/1DBurges/fig/ErrorComparsion_NResi.pdf}
\caption{The prediction accuracy of the Projection, POD-G, PINN and PRNN methods. $N_{Resi}$=1250, 2500, 5000, 10000 residual points are chosen for training the PINN and PRNN.}
\label{fig_1DBurgesErrorComparsion_NResi}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=9cm]{../../pythonNN/1DBurges/fig/ResultComparsion.pdf}
\caption{The comparison between the Chebyshev pseudospectral (PS) and the PRNN solutions for four specific parameters. The results of the PRNN are obtained via employing the $m$=9 modes extracted from 10 snapshot and a network of $L$=3 and $n_H$=20 architecture trained with 5000 residual points.}
\label{fig_1DBurgesResultComparsion}
\end{figure}
